Using Graphical Models for Novelty Detection on Semantic Room Classification

### 2011-05-10 semantic-nd/article.tex
changed fictitious for synthetic

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
In order to verify the improvements obtained by using unlabelled data, a fictitious simple
dataset was generated.
The fictitious distribution assumes that an independent and variable size set of features
$x$ is generated by a given room category.
In whole there was 11 different room categories and 7 different measured properties types.

@@

\caption{\label{fig:simple-experiment}The graph structures $G$ and $I$ used to model the
         conditional and unconditional probability.
         Note that graph $G$ correctly models the structure of the fictitious distribution, though
         during training it has not seen all possible room categories represented by variable $R_1$.}

@@

\caption{\label{fig:fictitious-roc}ROC curve comparing novelty detection performance between an optimal detector,
         $P_G(x)/P_U(x)$ a graph ratio considering an uniform unconditional distribution and
         $P_G(x)/P_I(x)$ a graph ratio considering an independent unconditional distribution}
\end{figure}

Since the distribution is fictitious its possible to create an optimal novelty detector, as
its the error rate $P(novel|x)$ can be exactly measured.
That serves as a comparison on how optimal a detector can be using the same input space.
A ROC curve was plotted for the three methods on \autoref{fig:fictitious-roc}.
As possible to see the unconditional probability plays an important role in obtaining a correct
ordering of the input space.

@@

\caption{\label{fig:fictitious-roc-breakdown}ROC curves plotted showing performance of the
         presented novelty detection method on graphs generated for different amount of
         sensed variables.
         As possible to see as the system gains more semantic information it becomes easier
         to detect novelty and the effect of picking an approximation for the unconditional
         probability decreases.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
In order to verify the improvements obtained by using unlabelled data, a synthetic dataset
was generated.
The synthetic distribution assumes that an independent and variable size set of features
$x$ is generated by a given room category.
In whole there was 11 different room categories and 7 different measured properties types.

@@

\caption{\label{fig:simple-experiment}The graph structures $G$ and $I$ used to model the
         conditional and unconditional probability.
         Note that graph $G$ correctly models the structure of the synthetic distribution, though
         during training it has not seen all possible room categories represented by variable $R_1$.}

@@

\caption{\label{fig:synthetic-roc}ROC curve comparing novelty detection performance between an optimal detector,
         $P_G(x)/P_U(x)$ a graph ratio considering an uniform unconditional distribution and
         $P_G(x)/P_I(x)$ a graph ratio considering an independent unconditional distribution}
\end{figure}

Since the distribution is synthetic its possible to create an optimal novelty detector, as
its the error rate $P(novel|x)$ can be exactly measured.
That serves as a comparison on how optimal a detector can be using the same input space.
A ROC curve was plotted for the three methods on \autoref{fig:synthentic-roc}.
As possible to see the unconditional probability plays an important role in obtaining a correct
ordering of the input space.

@@

\caption{\label{fig:synthetic-roc-breakdown}ROC curves plotted showing performance of the
         presented novelty detection method on graphs generated for different amount of
         sensed variables.
         As possible to see as the system gains more semantic information it becomes easier
         to detect novelty and the effect of picking an approximation for the unconditional
         probability decreases.}
\end{figure}
